---
output: 
  github_document:
    html_preview: FALSE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# bdist

[![Travis Build Status](https://travis-ci.org/kuperov/bdist.svg?branch=master)](https://travis-ci.org/kuperov/bdist)
[![Coverage Status](https://img.shields.io/codecov/c/github/kuperov/bdist/master.svg)](https://codecov.io/github/kuperov/bdist?branch=master)

This is a package of distributions I have found useful for
Bayesian analysis. Distributions include:

  * double generalized Pareto
  * Weibull (alternative parameterization)
  * student t (alternative parameterization)
  * truncated normal
  * multivariate normal
  * inverse gamma
  * inverse root gamma

All distributions include density, quantile, cdf, and generation functions, and all are unit tested.

Installation
------------

    library(devtools)
    install_github('kuperov/bdist')

Example
-------

Plot a double generalized Pareto distribution:

```{r 'dgp'}
  library(bdist)
  gdp.density <- function(x) dgdp(x, xi = 1, alpha = 2)
  plot(gdp.density, from = -5, to = 5, col = 'blue',
       main = expression("Double Generalized Pareto distribution:" ~
                           xi == 1~alpha == 2))
```

